Ensuring Fairness with Transparent Auditing of Quantitative Bias in AI Systems\\ \thanks{This project is partially supported by MOST111-2221-E-001-010-MY2 and 112-2634-F-002-004 from National Science and Technology Council and AS-GCS-113-H04 from Academia Sinica.}

### 2024-07-04 paper/paper.tex
Update funding source

\title{Ensuring Fairness with Transparent Auditing of Quantitative Bias in AI Systems\\
\thanks{This project is partially supported by NSTC 112-2634-F-002-004 from National Science and Technology Council and AS-GCS-113-H04 from Academia Sinica.}
}

>>>>

\title{Ensuring Fairness with Transparent Auditing of Quantitative Bias in AI Systems\\
\thanks{This project is partially supported by MOST111-2221-E-001-010-MY2 and 112-2634-F-002-004 from National Science and Technology Council and AS-GCS-113-H04 from Academia Sinica.}
}
